---
title: "R Notebook"
output: html_notebook
author : Kamaldeep Kaur
---


```{r}
#install.packages("Metrics")
#install.packages("car")
library(tseries)
library(plyr)
library(forecast)
library(tsutils)
library(imputeTS)
library(smooth)
library(tidyverse)
library(Metrics)
library(data.table)
library(car)
library(zoo)
library(xts)
#Load the data
#setwkdir
setwd("D:/Modules/Forecasting/CW2")
print(getwd())
data=read.csv("NN5-015.csv")
# create the sequence for ts object
inds=seq(as.Date("1996-03-18"),as.Date("1998-03-22"),by="day")
# Form ts object for modelling
ts_k=ts(data$Val,start=c(1996,as.numeric(format(inds[1],"%j"))),
        frequency = 365)
TSname="NN5-015"
Date <- seq(as.Date("1996-03-18"),as.Date("1998-03-22"),by="day")

# Timeseries1 :Seasonal impute with moving average
ts_k_wday_w=ts(ts_k,start=c(12,1),frequency = 7)
ts_k_impw=na_seasplit(ts_k_wday_w,algorithm ="ma")
ggplot_na_imputations(ts_k,ts_k_impw, title = paste("Imputed values with seasonal ma for", TSname))

# Timeseries2 : Seasonal impute with moving average With removed outlier 
ts_k_wday_w_nout=ts(replace(ts_k,641,NA),start=c(12,1),frequency = 7)
ts_k_impw_nout=na_seasplit(ts_k_wday_w,algorithm ="ma")

# Timeseries3 : Seasonal impute with moving average for 0 and missing values to asses multiplicative model and not outlier
test <- replace(ts_k,641,NA)
test <- as.data.frame(test)
test[test==0] <- NA
ts_k1=ts(test$x,start=c(1996,as.numeric(format(inds[1],"%j"))),frequency = 365)
ts_k_wday_w_m=ts(ts_k1,start=c(12,1),frequency = 7)
ts_k_impw_m=na_seasplit(ts_k_wday_w_m,algorithm ="ma")
```
# Split the data
```{r}
# Set horizon and number of rolling origins
h <- 30
origins <- 10  
step <- 7
ts_length <- length(ts_k_impw)
train_length <- ts_length - h - (origins*step) + 1   # multiply by 7 for multistep ahead validation
test_length <- h + (origins*step) - 1
print(train_length)
print(test_length)

# Split data for Timeseries1 with no missing values
ts_k_train <- ts(ts_k_impw[1:train_length],
frequency=frequency(ts_k_impw),
start=start(ts_k_impw))
ts_k_test <- ts(ts_k_impw[(train_length+1):ts_length])
# Split data for Timeseries2 with no missing values and no outlier
ts_k_train_nout <- ts(ts_k_impw_nout[1:train_length],
frequency=frequency(ts_k_impw_nout),
start=start(ts_k_impw_nout))
ts_k_test_nout <- ts(ts_k_impw_nout[(train_length+1):ts_length])
# Split data for Timeseries3 with no missing values and no outlier and no 0 valus for multiplicative trend test
ts_k_train_m <- ts(ts_k_impw_m[1:train_length],
frequency=frequency(ts_k_impw_m),
start=start(ts_k_impw_m))
ts_k_test_m <- ts(ts_k_impw_m[(train_length+1):ts_length])

```

#Functions 
```{r}
# Function to create out of sample data and hold out
Modeltest <- function(modelequ,ts_k_impw,ts_k_test,ModelName,forcstval= "forecast",origins= 10,h = 30,
                      step= 7, lag = 0)
{
ts_k_forecasts <- matrix(NA, nrow=origins, ncol=h)
ts_k_holdout <- matrix(NA, nrow=origins, ncol=h)

colnames(ts_k_forecasts) <- paste0("horizon",c(1:h))
rownames(ts_k_forecasts) <- paste0("origin",c(1:origins))
dimnames(ts_k_holdout) <- dimnames(ts_k_forecasts)
trainmetrix <- data.frame("MAE"= double(), "MSE"= double(),"MAPE"= double(),"RMSE"= double(), "WAPE"= double(),"AIC"= double())
testmetrix <- data.frame("MAE"= double(), "MSE"= double(),"MAPE"= double(),"RMSE"= double(),"WAPE"= double(),"AIC"= double())
for(i in 1:origins){
# Create a ts object out of the ts_k_impw data
  if (i != 1){j <- (i-1)*7} else {j <- i}
  train_set <- ts(ts_k_impw[1:(train_length+j-1)],
  frequency=frequency(ts_k_impw),
  start=start(ts_k_impw))
# Write down the holdout values from the test set
  ts_k_holdout[i,] <- ts_k_test[j-1+(1:h)]
# Produce forecasts and write them down
  modelfit <- eval(parse(text=modelequ))
  if (forcstval == "pred"){
  ts_k_forecasts[i,] <- eval(parse(text=paste("predict(modelfit)$",forcstval,sep="")))}
  else {
  ts_k_forecasts[i,] <- eval(parse(text=paste("modelfit$",forcstval,sep="")))
  }
# Error for out of sample data
  meanabserror <- mae(ts_k_holdout[i,],ts_k_forecasts[i,])
  meansqerror <- mse(ts_k_holdout[i,],ts_k_forecasts[i,])
  meanabspererror <- mape(ts_k_holdout[i,],ts_k_forecasts[i,])
  rootmeansqerror <- rmse(ts_k_holdout[i,],ts_k_forecasts[i,])
  wapeerror <- sum(abs(diff(ts_k_holdout[i,]-ts_k_forecasts[i,])))/sum(ts_k_holdout[i,])
  testmetrix[nrow(testmetrix) + 1,] = c(meanabserror,meansqerror,meanabspererror,rootmeansqerror,wapeerror,0)
# Error for In Sample data
  if (forcstval=="pred"){ 
    fittedVal <- fitted.values(modelfit)[(lag+1):length(fitted.values(modelfit))]
}
  else {fittedVal <- modelfit$fitted[(lag+1):length(modelfit$fitted)]}
  actualVal <- train_set[(lag+1):length(train_set)]
  meanabserror1 <- mae(actualVal,fittedVal)
  meansqerror1 <- mse(actualVal,fittedVal)
  meanabspererror1 <- mape(actualVal,fittedVal)
  rootmeansqerror1 <- rmse(actualVal,fittedVal)
  wapeerror1 <- sum(abs(diff(actualVal-fittedVal)))/sum(actualVal)
  if (forcstval=="mean"){modelAIC <- 0}
  else {  modelAIC <- AIC(modelfit)}
  trainmetrix[nrow(trainmetrix) + 1,] = c(meanabserror1,meansqerror1,meanabspererror1,rootmeansqerror1,wapeerror1,modelAIC)
}
Testerror <- round(colMeans(testmetrix),2)
Trainerror <- round(colMeans(trainmetrix),2)
errmet <- rbind(cbind(Model=ModelName,Sample="In Sample",t(Trainerror)),cbind(Model=ModelName,Sample="Out Sample",t(Testerror)))
return(errmet)
}

```
# Naive and Seasonal Naive
```{r}
#Naive
ErrmatN <- Modeltest("naive(train_set,h = h)",ts_k_impw,ts_k_test,ModelName ="Naive",forcstval = "mean",lag = 1)
print(ErrmatN)
#SNaive
ErrmatSN <- Modeltest("snaive(train_set,h = h)", ts_k_impw,ts_k_test,ModelName ="SNaive",forcstval = "mean", lag =7)
print(ErrmatSN)
# Plot 14 days forecast
print(getwd())
SNaiveforecast <- snaive(ts_k_impw,h = 14)
jpeg("SNaive forecast.jpg")
plot(SNaiveforecast)
dev.off()

```
# Exponential Smoothing Models
```{r}
# Additive Error term, No Trend, Additive Seasonality model
ErrmatES1 <- Modeltest("es(train_set, model='MAM', h = h, holdout= FALSE)",ts_k_impw_m,ts_k_test_m,ModelName ="ESMAM")
print(ErrmatES1)
# Additive Error term, No Trend, Multiplicative Seasonality model
ErrmatES2 <- Modeltest("es(train_set, model='ANM', h = h, holdout= FALSE)",ts_k_impw_m,ts_k_test_m,ModelName ="ESANM")
print(ErrmatES2) # SO far best model
# Additive Error term, Additive Trend, Additive Seasonality model
ErrmatES3 <- Modeltest("es(train_set, model='AAA', h = h, holdout= FALSE)",ts_k_impw_m,ts_k_test_m,ModelName ="ESAAA")
print(ErrmatES3)
# Additive Error term, Additive Trend, Multiplicative Seasonality model
ErrmatES4 <- Modeltest("es(train_set, model='AAM', h = h, holdout= FALSE)",ts_k_impw_m,ts_k_test_m,ModelName ="ESAAM")
print(ErrmatES4)
# Additive Error term, No Trend, Multiplicative Seasonality model, with manually estimated coefficients
ErrmatES5 <- Modeltest("es(train_set, model='ANM', h = h, holdout= FALSE,persistence= c(0.07,0.26))",ts_k_impw_m,ts_k_test_m,ModelName ="ESANMSelCoeff")
print(ErrmatES5)
# Auto Selected ETS with Multiplicative Error term, No Trend, Multiplicative Seasonality
ErrmatES6 <- Modeltest("es(train_set,model = 'MNM',h = h, holdout=  FALSE)",ts_k_impw_m,ts_k_test_m,ModelName ="ESMNMAuto")
print(ErrmatES6)
```
# Find Coefficient of ESANM 
```{r}
# Validate model 2 coefficient
ESANM <- es(ts_k_impw_m, model='ANM', h = h, holdout= TRUE,silent= "none")
print(coef(ESANM))
summary(ESANM)

# Change in gamma and alpha
ESANMerror <- data.frame("Alpha" = double(),"Gamma"= double(),"MAPE"= double(),"RMSE"= double(), "AIC"= double())
for ( a in seq(0.01,1,by=0.05)){
  for ( g in seq(0.01, 1, by= 0.05)){
    #print(paste(a,g))
    ESANM <- es(ts_k_impw_m, model='ANM', h = 30, persistence= c(a,g) , holdout= TRUE)
  ESANMerror <- rbind(ESANMerror,c(Alpha=a,Gamma=g,MAPE=ESANM$accuracy["MAPE"],RMSE= ESANM$accuracy["rRMSE"], AIC = ESANM$ICs[1]))
  }
}
colnames(ESANMerror) <- c("Alpha","Gamma","MAPE","RMSE","AIC")
#checkresiduals(ESANM)
# For constant alpha
ESANMerror_gamma <- data.frame("Alpha" = double(),"Gamma"= double(),"MAPE"= double(),"RMSE"= double(),"AIC" = double())
for ( g in seq(0.01, 1, by= 0.05)){
    #print(paste(a,g))
    ESANMgamma <- es(ts_k_impw_m, model='ANM', h = 30, persistence= c(0.07,g) , holdout= TRUE)
  ESANMerror_gamma <- rbind(ESANMerror_gamma,c(Alpha=0.07,Gamma=g,MAPE=ESANMgamma$accuracy["MAPE"],RMSE= ESANMgamma$accuracy["rRMSE"],AIC = ESANMgamma$ICs[1]))
}
colnames(ESANMerror_gamma) <- c("Alpha","Gamma","MAPE","RMSE","AIC")
ggplot(ESANMerror_gamma, aes(x= Gamma,y = MAPE)) + geom_line()+ geom_point()
ggplot(ESANMerror_gamma, aes(x= Gamma,y = AIC)) + geom_line()+ geom_point()
# For constant gamma
ESANMerror_alpha <- data.frame("Alpha" = double(),"Gamma"= double(),"MAPE"= double(),"RMSE"= double(),"AIC"= double())
for ( a in seq(0.02,1,by=0.05)){
    ESANMalpha <- es(ts_k_impw_m, model='ANM', h = 30, persistence= c(a,0.75) , holdout= TRUE)
  ESANMerror_alpha <- rbind(ESANMerror_alpha,c(Alpha=a,Gamma=0.26,MAPE=ESANMalpha$accuracy["MAPE"],RMSE= ESANMalpha$accuracy["rRMSE"],AIC = ESANMgamma$ICs[1]))
}
colnames(ESANMerror_alpha) <- c("Alpha","Gamma","MAPE","RMSE","AIC")
ggplot(ESANMerror_alpha, aes(x= Alpha,y = MAPE)) + geom_line()+ geom_point()
ggplot(ESANMerror_alpha, aes(x= Alpha,y = AIC)) + geom_line()+ geom_point()

# Estimated alpha and gamma
#alpha =  0.07
#gamma = 0.75

#Model AAM for residual plot 
ESAAM_estcoff <- es(ts_k_impw_m, model='AAM', h = h, holdout= TRUE)
jpeg("ETSAAM_Residuals.jpg")
ggtsdisplay(ESAAM_estcoff$residuals, lag= 200 , main = "ETSAAM Residuals")
dev.off()
checkresiduals(ESAAM_estcoff)
qqplot()
#Model coefficients estimated by computer 
ESMAM_estcoff <- es(ts_k_impw_m, model='MAM', h = h, holdout= TRUE)
jpeg("ETSMAM_Residuals.jpg")
ggtsdisplay(ESMAM_estcoff$residuals, lag= 100, main = "ETSMAM Residuals")
#checkresiduals(ESMAM_estcoff)
dev.off()
# alpha- 0.0157 gamma - 0.0000
# Model with manually estimated coefficients
ESANM_predefcoff <- es(ts_k_impw_m, model='ANM', h = h,persistence= c(0.07,0.26), holdout= TRUE)
summary(ESANM_predefcoff)
# Auto Selecetd Model 
ESMNM_Auto<- es(ts_k_impw_m, model='MNM', h = h, holdout= TRUE)
summary(ESMNM_Auto)
jpeg("ETSMNM_Residuals.jpg")
#ggtsdisplay(ESMNM_Auto$residuals, lag= 200, main = "ETSMNM Residuals")
checkresiduals(ESMNM_Auto)
dev.off()
checkresiduals(ESMNM_Auto)

```

# ARIMA Model 
```{r}
plot(decompose(ts_k_impw_nout))
jpeg("Original_TimeSeries_ACFPACF.jpg")
ggtsdisplay(ts_k_impw_nout,main = "Original Time Series ACF PACF")
dev.off()
#1 difference for trend
diff_ts_k_impw <- diff(ts_k_impw_nout)
jpeg("ARIMA Difference_Residuals.jpg")
ggtsdisplay(diff_ts_k_impw,lag = 30,main ="Residuals from 1st difference")
dev.off()
kpss.test(diff_ts_k_impw)  # both test suggests stationarity 
adf.test(diff_ts_k_impw)
#Apply 7 days seasonal SARIMA with 1 diif
#SARIMA(0,1,0)(0,1,0))
fit1 <- Arima(ts_k_impw_nout, order=c(0,1,0), seasonal=c(0,1,0))
jpeg("ARIMA SeasonalDiff_Residual.jpg")
ggtsdisplay(residuals(fit1), lag = 50,main="Fit1 - Residuals from ARIMA(0,1,0)(0,1,0)")
dev.off()
#checkresiduals(fit1,plot = TRUE)
#SARIMA(0,1,0)(0,1,1))
fit2 <- Arima(ts_k_impw_nout, order=c(0,1,0), seasonal=c(0,1,1))
jpeg("ARIMA 7SMASeasonalDiff_Residual.jpg")
ggtsdisplay(residuals(fit2), lag= 100,main="Fit2 - Residuals from ARIMA(0,1,0)(0,1,1)")
dev.off()
#checkresiduals(residuals(fit2),plot = TRUE)
#SARIMA(0,1,1)(0,1,1))
fit3 <- Arima(ts_k_impw_nout, order=c(0,1,1), seasonal=c(0,1,1))
jpeg("ARIMA 1MA 7SMASeasonalDiff_Residual.jpg")
ggtsdisplay(residuals(fit3), lag= 100,main="Fit3 - Residuals from ARIMA(0,1,1)(0,1,1)")
dev.off()
#checkresiduals(fit3,plot = TRUE)
print(Box.test(residuals(fit3), lag = 1, type = "Ljung-Box"))
#SARIMA(6,1,6)(0,1,0))
fit4 <- arima(ts_k_impw_nout, order=c(1,1,1), seasonal=c(0,1,1))
jpeg("ARIMA 1AR 1MA 7SMASeasonalDiff_Residual.jpg")
ggtsdisplay(residuals(fit4), lag= 300,main="Fit4 - Residuals from ARIMA(1,1,1)(0,1,1)")
dev.off()
#checkresiduals(residuals(fit4),plot= TRUE)
print(Box.test(residuals(fit4), lag = 1, type = "Ljung-Box"))

#Auto ARIMA
fit5 <- auto.arima(ts_k_impw_nout)
jpeg("ARIMA Auto_Residual.jpg")
ggtsdisplay(residuals(fit5), lag= 300,main="Fit5 -Residuals from Auto ARIMA(1,0,0)(0,1,1)")
dev.off()
print(Box.test(residuals(fit5), lag = 1, type = "Ljung-Box"))
#checkresiduals(residuals(fit5),plot= TRUE)

# Run Both ARIMA models for Rolling Origin
ARIMASelected <- Modeltest("arima(train_set,order=c(1,1,1), seasonal=c(0,1,1))",forcstval="pred" ,ts_k_impw_nout,ts_k_test_nout,ModelName ="ARIMA(111)(011)")
print(ARIMASelected)
# Auto Selected
ARIMAAuto <- Modeltest("arima(train_set,order=c(1,0,0), seasonal=c(0,1,1))",forcstval="pred" ,ts_k_impw_nout,ts_k_test_nout,ModelName ="ARIMA(100)(011)")
print(ARIMAAuto)

```

# Prepare data for Regression Using Dummy variables and Lags
```{r}
# Total 735 observaltion, dor weekday dummies we need repeatation = 105(735/7)
D1 <- rep(c(1,0,0,0,0,0,0),105)
D2 <- rep(c(0,1,0,0,0,0,0),105)
D3 <- rep(c(0,0,1,0,0,0,0),105)
D4 <- rep(c(0,0,0,1,0,0,0),105)
D5 <- rep(c(0,0,0,0,1,0,0),105)
D6 <- rep(c(0,0,0,0,0,1,0),105)
D7 <- rep(c(0,0,0,0,0,0,1),105)
Dout <- rep(c(0),735)
Dout[641] <- 1 # Set 1 for outlier 

Reg_data <- as.data.frame(cbind(ts_k_impw,D1,D2,D3,D4,D5,D6,D7,Dout))
colnames(Reg_data) <- c("ATMW","D1","D2","D3","D4","D5","D6","D7","Dout")
Reg_data$L7_ATMW <- shift(Reg_data$ATMW,n = 7,fill= NA, type="lag")
Reg_data$L1_ATMW <- shift(Reg_data$ATMW,n = 1,fill= NA, type="lag")
Reg_data$L2_ATMW <- shift(Reg_data$ATMW,n = 2,fill= NA, type="lag")
Reg_data$Trend <-  c(1:nrow(Reg_data))

```
# Regression Function with Intial data split 
```{r}
RegmodelCV <- function(df,frm="ATMW~.",ModelName,origins=10,h=30,step=7,lag=0) {
#Split Data
Reg_data = df
origins = origins
h = h
step = step
df_length <- nrow(Reg_data)
dftrain_length <- df_length - h - (origins*step) + 1   # multiply by 7 for multistep ahead validation
dftest_length <- h + (origins*step) - 1
Reg_test <- slice_tail(Reg_data, n=dftest_length)
reg_forecasts <- matrix(NA, nrow=origins, ncol=h)
reg_holdout <- matrix(NA, nrow=origins, ncol=h)
ICs <- matrix(NA,nrow=origins,ncol=3)

colnames(ICs) <- c("AIC","AICc","BIC")
colnames(reg_forecasts) <- paste0("horizon",c(1:h))
rownames(reg_forecasts) <- paste0("origin",c(1:origins))
dimnames(reg_holdout) <- dimnames(reg_forecasts)
regtestmetrix <- data.frame("MAE"= double(), "MSE"= double(),"MAPE"= double(),"RMSE"= double(),"WAPE"=double(),"AIC"= double())
regtrainmetrix <- data.frame("MAE"= double(), "MSE"= double(),"MAPE"= double(),"RMSE"= double(),"WAPE"=double(),"AIC"= double())
# Out of Sample cross validation 
for(i in 1:origins){
# Create a ts object out of the ts_k_impw data
  if (i != 1){j <- (i-1)*7} else {j <- i}
  train_set <- Reg_data[seq(1,(dftrain_length+j-1)),]
  test_start <- nrow(train_set)+1
  test_set <- Reg_data[seq(test_start,test_start+h-1),]
# Write down the holdout values from the test set
  reg_holdout[i,] <- test_set$ATMW
  # Regression model with all dummy variables
  Rgfit1 <- lm(formula=frm, data=train_set)
  ICs[i,] <- c(AIC(Rgfit1),AICc(Rgfit1),BIC(Rgfit1))
  fitted_train <- Rgfit1$fitted.values
  actual_train <- train_set$ATMW[(lag+1):dim(train_set)[1]]
  # Produce forecasts and write them down
  regpred <- predict(Rgfit1,newdata = subset(test_set,select=-ATMW))
    reg_forecasts[i,] <- regpred 
  # Prepare test error data
  meanabserror <- mae(reg_holdout[i,],reg_forecasts[i,])
  meansqerror <- mse(reg_holdout[i,],reg_forecasts[i,])
  meanabspererror <- mape(reg_holdout[i,],reg_forecasts[i,])
  rootmeansqerror <- rmse(reg_holdout[i,],reg_forecasts[i,])
  wapeerror <- sum(abs(diff(reg_holdout[i,]-reg_forecasts[i,])))/sum(reg_holdout[i,])
  regtestmetrix[nrow(regtestmetrix) + 1,] = c(meanabserror,meansqerror,meanabspererror,rootmeansqerror,wapeerror,0)
  # Prepare Train error data
  meanabserror1 <- mae(actual_train,fitted_train)
  meansqerror1 <- mse(actual_train,fitted_train)
  meanabspererror1 <- mape(actual_train,fitted_train)
  rootmeansqerror1 <- rmse(actual_train,fitted_train)
  wapeerror1 <- sum(abs(diff(actual_train-fitted_train)))/sum(actual_train)
  regtrainmetrix[nrow(regtrainmetrix) + 1,] = c(meanabserror1,meansqerror1,meanabspererror1,rootmeansqerror1,wapeerror1,AIC(Rgfit1) )
}
Testerror <- round(colMeans(regtestmetrix),2)
errmet <- rbind(cbind(Model=ModelName,Sample="In Sample",t(Trainerror)),cbind(Model=ModelName,Sample="Out Sample",t(Testerror)))
retval <- list(errmet,round(Rgfit1$residuals))
return(retval)
}

```
# Run regression Models
```{r}
# Correlation Metrix for dummy seasonal variables
cor(subset(Reg_data,select= c(D1,D2,D3,D4,D5,D6)))
# Models test 
Rgfit1 <- lm(ATMW~D1+D2+D3+D4+D5+D6, data=Reg_train)
#print(vif(Rgfit1))
Rgfit2 <- lm(ATMW~D1+D2+D3+D4+D6+L7_ATMW+L1_ATMW, data=Reg_train)
print(vif(Rgfit2))
print(summary(Rgfit2))
print(Box.test(residuals(Rgfit2), lag = 1, type = "Ljung-Box"))
Rgfit3 <- lm(ATMW~D1+D3+D4+D6+L7_ATMW+L1_ATMW+Dout+Trend, data=Reg_train)
print(vif(Rgfit3))
print(Box.test(residuals(Rgfit3), lag = 1, type = "Ljung-Box"))

# Estimate avergae error metrics using rolling origin 
# MOdel 1
RgdummyLag71 <- RegmodelCV(Reg_data,frm="ATMW~D1+D2+D3+D4+D6+L7_ATMW+L1_ATMW+Dout",ModelName="Reg dummy and Lag",origins=10,h=30,step=7, lag= 7)
print(RgdummyLag71[1])
#tsdisplay(ts(Rgdummy[[3]],start=c(12,1),frequency = 7),lag=100)
# Regression with seasonal lag
RgdummyLagOtrend <- RegmodelCV(Reg_data,frm="ATMW~D1+D3+D4+D6+L7_ATMW+L1_ATMW+Dout+Trend",ModelName=" Reg dummy,Lag,Trend,Outlier", origins=10,h=30,step=7, lag=7)
print(RgdummyLagOtrend[1])
jpeg("RegressionEstimated_Residuals.jpg")
ggtsdisplay(ts(unlist(RgdummyLagOtrend[2]),start=c(12,1),frequency = 7),lag=300,main ="RgFit2-Regression Selected variable Residuals")
dev.off()
#tsdisplay(ts(Rgdummylag71[[3]],start=c(12,1),frequency = 7),lag=100)

```
# Auto selection of variables for Regression
```{r}
model <- lm(ATMW~.,data = Reg_data)
Autoselect <- step(model,direction= "backward", k =2)
# Model from backward selection 
#AIC = 1992
#ATMW ~ D1 + D3 + D4 + D6 + L7_ATMW + L1_ATMW + Trend
RgAutosel <- RegmodelCV(Reg_data,frm="ATMW ~ D1 + D3 + D4 + D6 +Dout+ L7_ATMW + L1_ATMW + Trend",ModelName= "Reg Auto",origins=10,h=30,step=7,lag = 7)
print(RgAutosel[1])
jpeg("RegressionAuto_Residuals.jpg")
ggtsdisplay(ts(unlist(RgAutosel[2]),start=c(12,1),frequency = 7),lag=300,main ="Regression Auto Residuals")
dev.off()
```

# Neural Network Forescasting Model 
```{r}

nnmodel = nnetar(ts_k_impw, repeats =30,P = 7)
NNtest <- Modeltest("forecast::forecast(nnetar(train_set,repeats =30,P = 7),h)",ts_k_impw, ts_k_test,ModelName="NeuralNetwork", forcstval = "mean")
print(NNtest)
NNforecast <- forecast::forecast(nnmodel,h=14)
jpeg("NN Forecast.jpg")
plot(NNforecast)
dev.off()
jpeg("NN Residuals.jpg")
ggtsdisplay(nnmodel$residuals,lag = 100, main= "NN Residuals")
dev.off()

```

# Plot all models together for 30 holdout
```{r}
# Split data for ARIMA and Naive
final.train <- ts(ts_k_impw[1:705],
           frequency=frequency(ts_k_impw),
           start=start(ts_k_impw))
final.test <- ts(ts_k_impw[(706):735])
#Split data for regression 
Reg_train <- Reg_data[1:705,]
Reg_test <- Reg_data[706:735,]
#Splitr data for exponential smoothing 
ESfinal.train <- ts(ts_k_impw_m[1:705],
           frequency=frequency(ts_k_impw_m),
           start=start(ts_k_impw_m))
ESfinal.test <- ts(ts_k_impw_m[(706):735])

# Fit different models smoothing as predict 30 days decided earlier
SESautocoeff <- es(ESfinal.train, model='MNM', h = 30)
ARIMA <- arima(final.train, order=c(1,1,1), seasonal=c(0,1,1))
arimapred <- predict(ARIMA,30)
Rgfit1 <- lm(ATMW~D1+D3+D4+D6+L7_ATMW+L1_ATMW+Dout+Trend, data=Reg_train)
regpred <- predict(Rgfit1,newdata = subset(Reg_test,select=-ATMW))
regpredci <- predict(Rgfit1,newdata = subset(Reg_test,select=-ATMW), interval = "prediction", level = 0.95)
SNaiveforecast <- snaive(final.train,h = 30)
NNforecast <- forecast::forecast(nnetar(final.train, repeats =30,P = 7),h=30)

# Forecast for all models in one dataframe for plotting
df <- data.frame(dt = Date[706:735],Original= final.test,ESMNM = SESautocoeff$forecast,Rgression = regpred, SARIMA = arimapred$pred, NN = NNforecast$mean, SNaive = SNaiveforecast$mean )
df1 <- reshape2::melt(df, id.vars = "dt", measure.vars = c("Original","ESMNM","Rgression","SARIMA","NN","SNaive"))
colnames(df1) <- c("Date","Models","ATMWithdrawl")
df$Original <- ts(df$Original, start=c(112,6), frequency = 7)
RMSE <- c(rmse(df$Original,df$SNaive),rmse(df$Original,df$ESMNM),rmse(df$Original,df$Rgression),rmse(df$Original,df$SARIMA),rmse(df$Original,df$NN))
print(RMSE)

ggplot(data= df1,aes(x= Date, y = ATMWithdrawl, color= Models))+
  geom_line() + ggtitle(label="Model prediction for 30 days")
ggsave("All Models.jpg")

ggplot(data= df1 %>% filter(Models %in% c("Original", "ESMNM")) ,aes(x= Date, y = ATMWithdrawl, color= Models))+
  geom_line() + ggtitle(label="Out-of-Sample Forecast for ES")
ggsave("Final ESMNM comparsion.jpg")


```
# Predict 14 values for all models
```{r}
# Regression 
# Extrapolate and Forecast of Lag ATM withdrawls
ATMLag7 <- es(ts(Reg_data$L7_ATMW, frequency = 7),model='ANA',h= 14, holdout=FALSE)
ATMLag1 <- es(ts(Reg_data$L1_ATMW, frequency = 7),model='ANA',h= 14, holdout=FALSE)
D1f <- rep(c(1,0,0,0,0,0,0),2)
D2f <- rep(c(0,1,0,0,0,0,0),2)
D3f <- rep(c(0,0,1,0,0,0,0),2)
D4f <- rep(c(0,0,0,1,0,0,0),2)
D5f <- rep(c(0,0,0,0,1,0,0),2)
D6f <- rep(c(0,0,0,0,0,1,0),2)
D7f <- rep(c(0,0,0,0,0,0,1),2)
Dof <- rep(c(0),14)
Trend <- seq(736,749)
dfforecast <- data.frame(cbind(D1f,D2f,D3f,D4f,D5f,D6f,D7f,c(ATMLag7$forecast),c(ATMLag1$forecast),Dof,Trend))
colnames(dfforecast) <- c("D1","D2","D3","D4","D5","D6","D7","L7_ATMW","L1_ATMW","Dout","Trend")
# Fit Model 
Rgfit1 <- lm(ATMW ~ D1 + D3 + D4 + D6 +Dout+ L7_ATMW + L1_ATMW + Trend, data=Reg_data)
Regforcast <- predict(Rgfit1,newdata=dfforecast)
ggplot(data= data.frame(cbind(index=seq(1,14),Forecast= Regforcast)))+ geom_line(aes(x=index,y=Forecast )) + ggtitle("Regression Forecast for 14 days")
ggsave("Regression 14 days.jpg")
```
# 14 Forecast ES and ARIMA other models
```{r}
# Forecast unseen 14 days
ESforecast <- es(ts_k_impw_m, model='MAM', h = 14)
ARIMA <- arima(ts_k_impw, order=c(1,1,1), seasonal=c(0,1,1))
dfforecast <- as.data.frame(cbind(index=seq(1,14),ESforecast$forecast,ARIMAforecast$pred))
colnames(dfforecast) <- c("Index","ESForecast","ARIMAForecast")
# Print Forecast from all models
ggplot(data= dfforecast)+ geom_line(aes(x=Index,y= ESForecast )) + ggtitle("Exponential Smoothing MNM Forecast for 14 days")
ggsave("ES 14 days.jpg")
ggplot(data= dfforecast)+ geom_line(aes(x=Index,y=ARIMAForecast )) + ggtitle("ARIMA(1,1,1)(0,1,1) Forecast for 14 days")
ggsave("ARIMA 14 days.jpg")
```

